**Best practices for applying machine learning to bacterial 16S rRNA gene sequencing data**

### 2019-08-16 submission/manuscript.Rmd
changes to fig 3

We interpreted the feature importance in the linear models (L1 and L2-regularized SVM with linear kernel and L2-regularized logistic regression) using the median absolute feature weights for each OTU in the models [Figure 3]. The OTUs that had the largest median rank and drove the detection of SRNs across the linear models contained sequences that were most similar to members of the Lachnospiraceae (OTU 1239, OTU 742), Roseburia (OTU 822, OTU00768), Clostridium (OTU 609), Blautia (OTU 659, OTU 12), Faecalibacterium (OTU 15), Gamella (OTU 426) and Peptostreptococcus (OTU 367) [Figure 3]. Among the five highest ranked OTUs across these three models, it was encouraging that OTU 1239 was shared among each of the models and that 4 OTUs were shared among the five highest ranked OTUs for both of the L2-regularized models.

>>>>

We interpreted the feature importance in the linear models (L1 and L2-regularized SVM with linear kernel and L2-regularized logistic regression) using the median rank of absolute feature weights for each OTU in the models [Figure 3]. The OTUs that had the largest median rank and drove the detection of SRNs across the linear models contained sequences that were most similar to members of the Lachnospiraceae (OTU 1239, OTU 742), Roseburia (OTU 822, OTU00768), Clostridium (OTU 609), Blautia (OTU 659, OTU 12), Faecalibacterium (OTU 15), Gamella (OTU 426) and Peptostreptococcus (OTU 367) [Figure 3]. Among the five highest ranked OTUs across these three models, it was encouraging that OTU 1239 was shared among each of the models and that 4 OTUs were shared among the five highest ranked OTUs for both of the L2-regularized models.
